Symmetric Peer-to-Peer Applications

### 2022-08-27 tpd-22.tex
...

\begin{figure*}[t]
  \centering
  \includegraphics[width=\linewidth]{algos}
  \caption{
    \label{fig.algos}
    Four approaches to symmetric distributed applications: Croquet, GALS,
    CRDTs, and this work.
    The vertical arrows in parallel represent the timelines in nodes in the
    network.
    The arrows crossing nodes represent communication between them.
  }
\end{figure*}

@@

In this section, we describe the architecture of our middleware and also the
API in which developers have to conform with.
The middleware is written in C and relies on the library \emph{SDL}%
\footnote{SDL: \url{www.libsdl.org}}
to deal with the network and input events, such as timers, mouse clicks and
key presses.
The full source code%
\footnote{TODO}
is under 500 lines of code.

@@

@@

{\footnotesize
\begin{verbatim}
struct {
    int x,  y;   // position
    int dx, dy;  // direction speed
} G;
int main (void) { ... }
\end{verbatim}
}

@@

{\footnotesize
\begin{verbatim}
int cb_evt (SDL_Event* sdl, p2p_evt* evt) {
    if (sdl->type == SDL_KEYDOWN) {
        if (sdl->key == <any-of-the-keys>) {
            SDL_DrawImage(<img-of-the-key>);
            *evt = (p2p_evt) { P2P_EVT_KEY, sdl->key };
            return 1; // generate application event
        }
    }
    return 0; // otherwise, does not generate any event
}
\end{verbatim}
}

@@

\subsection{The Time Machine}
\label{sec.tml.time}

>>>>

\begin{figure*}[p]
  \centering
  \includegraphics[width=\linewidth]{algos}
  \caption{
    \label{fig.algos}
    Four approaches to symmetric distributed applications: Croquet, GALS,
    CRDTs, and this work.
    The vertical arrows in parallel represent the timelines in nodes in the
    network.
    The arrows crossing nodes represent communication between them.
  }
\end{figure*}

@@

In this section, we describe the architecture of our middleware and also the
API in which developers have to conform with.
%
The middleware is written in C and relies on the library \emph{SDL}%
\footnote{SDL: \url{www.libsdl.org}}
to deal with the network and input events, such as timers, mouse clicks and
key presses.
The full source code%
\footnote{TODO}
is under 500 lines of code.

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\linewidth]{middleware}
  \caption{
    Applications generate asynchronous events and communicate through an API
    with the middleware.
    The middleware orchestrates the peers, synchronizing their ticks locally
    and broadcasting events with a delay.
    \label{fig.middleware}
  }
\end{figure}

In Figure~\ref{fig.middleware}, a peer is depicted as an application that uses
an API to communicate with the middleware.
The application itself is not aware of the network and has no direct access to
the other peers, which communicate transparently through the middleware.
The application generates asynchronous events that go through the middleware,
which synchronizes them with a timestamp in the future, such that all peers can
agree.
The middleware controls the execution of the application by issuing ticks and
synchronized events.

@@

{\footnotesize
\begin{verbatim}
struct {
    int x,  y;   // position
    int dx, dy;  // direction speed
} G;
\end{verbatim}
}

@@

{\footnotesize
\begin{verbatim}
int cb_evt (SDL_Event* sdl, p2p_evt* evt) {
    if (sdl->type == SDL_KEYDOWN) {
        if (sdl->key == <any-of-the-keys>) {
            SDL_DrawImage(<img-of-the-key>);
            *evt = (p2p_evt){ P2P_EVT_KEY,sdl->key };
            return 1; // generate application event
        }
    }
    return 0; // otherwise, do not generate any event
}
\end{verbatim}
}

@@

\subsection{Middleware Orchestration}
\label{sec.tml.middleware}

We now describe in detail how the middleware orchestrates an application and
ensures that all peers (a) meet event deadlines, (b) advance in sync in real
time, and (c) can leave and join the network and remain symmetric.
